Cloud Supercomputing

### 2019-04-03 writing/paper/paper.tex
Added/Removed todos. Added introduction for AMR criterion

\section{Methods}
\todo{Write \aderdg{}/\exahype{} section! Riemann solver + timestep}
Maybe numerics (dg+muscl?), at least ref.
Exahype?! \todo{LR: Die Engine würde ich vor der Formel beschreibung machen: Also erst was macht die Engine, dann wie haben wir sie angewandt.}

We use the \aderdg{}-scheme as proposed in \cite{dumbser2008unified} together with a Rusanov-style flux~\cite{gassner2008discontinuous,fambri2017space} that is adapted for \pde{}s with diffusive terms.

Let $\bm{f}(\bm{x}): \mathbb{R}^{N_\text{vars}} \to \mathbb{R}$ be a function that maps the discrete solution at a point $\bm{x}$ to an arbitrary indicator variable.
The total variation (\textsc{tv}) of this function is defined by
\begin{equation}
  \label{eq:tv}
  \tv \left[ f(\bm{x}) \right] =
  \Vert
\intdcell{ \vert \gradient{f \left( \bm{x} \right)} \vert }
\Vert_1
\end{equation}
for each cell.
The operator $\Vert \cdot \Vert_1$ denotes the discrete $l_1$ norm in this equation.
We compute the integral efficiently with Gaussian quadrature over the collocated quadrature points.
\newcommand{\mean}{\mu}%
\newcommand{\std}{\sigma}%
\newcommand{\variance}{\std^2}%
\newcommand{\Trefine}{T_\text{refine}}%
\newcommand{\Tdelete}{T_\text{delete}}%
How can we decide whether a cell is important or not?
To resolve this conundrum, we compute the mean and the population standard deviation of the total variation of all cells.
It is important to note that we use the method of~\cite{chan1982updating} to compute the modes in a parallel and numerical stable manner.
A cell is then considered to contain significant information if its deviates from the mean more than a given threshold.
This criterion can be described formally by
\begin{equation}
  \label{eq:refinement-criterion}
  \operatorname{evaluate-refinement}(\Q, \mu, \sigma) =
  \begin{cases}
    \text{refine} & \text{if } \tv(\Q) \geq \mu + \Trefine \sigma \\
    \text{delete} & \text{if } \tv(\Q) < \mu + \Tdelete \sigma \\
    \text{keep} & \text{otherwise}.
    \end{cases}
\end{equation}
The parameters $\Trefine > \Tdelete$ can be chosen freely.
Chebyshev's inequality
\begin{equation}
  \label{eq:chebychev}
  \mathbb{P}(\vert X - \mu \vert \geq c \sigma) \leq \frac{1}{c^2},
\end{equation}
with probability $\mathbb{P}$ guarantees that we neither refine nor delete all cells. \todo{LR: Was gibt es an compressible NS mit dynamic AMR, wie unterscheiden wir uns im Refinement Kriterium?}
This inequality holds for arbitrary distributions under the weak assumption that their mean $\mu$ and standard deviation $\sigma$ are finite~\cite{wasserman2004all}.

>>>>

\section{Methods}
\todo{Write \aderdg{}/\exahype{} section! Riemann solver + timestep. LR: Was sollen wir da deiner Meinung nach noch erwähnen?}
Maybe numerics (dg+muscl?), at least ref.
Exahype?! 
We use the \aderdg{}-scheme as proposed in \cite{dumbser2008unified} together with a Rusanov-style flux~\cite{gassner2008discontinuous,fambri2017space} that is adapted for \pde{}s with diffusive terms. 
\todo{LR: Hier würde ich noch ein paar einleitende Worte hinzufügen}

Rules for dynamic AMR can be stated by the user with element wise checks against a custom defined set of criteria. We use an element local error estimate based on the total variation of the numerical solution. 
Let $\bm{f}(\bm{x}): \mathbb{R}^{N_\text{vars}} \to \mathbb{R}$ be a function that maps the discrete solution at a point $\bm{x}$ to an arbitrary indicator variable.
The total variation (\textsc{tv}) of this function is defined by
\begin{equation}
  \label{eq:tv}
  \tv \left[ f(\bm{x}) \right] =
  \Vert
\intdcell{ \vert \gradient{f \left( \bm{x} \right)} \vert }
\Vert_1
\end{equation}
for each cell.
The operator $\Vert \cdot \Vert_1$ denotes the discrete $l_1$ norm in this equation.
We compute the integral efficiently with Gaussian quadrature over the collocated quadrature points.
\newcommand{\mean}{\mu}%
\newcommand{\std}{\sigma}%
\newcommand{\variance}{\std^2}%
\newcommand{\Trefine}{T_\text{refine}}%
\newcommand{\Tdelete}{T_\text{delete}}%
How can we decide whether a cell is important or not?
To resolve this conundrum, we compute the mean and the population standard deviation of the total variation of all cells.
It is important to note that we use the method of~\cite{chan1982updating} to compute the modes in a parallel and numerical stable manner.
A cell is then considered to contain significant information if its deviates from the mean more than a given threshold.
This criterion can be described formally by
\begin{equation}
  \label{eq:refinement-criterion}
  \operatorname{evaluate-refinement}(\Q, \mu, \sigma) =
  \begin{cases}
    \text{refine} & \text{if } \tv(\Q) \geq \mu + \Trefine \sigma \\
    \text{delete} & \text{if } \tv(\Q) < \mu + \Tdelete \sigma \\
    \text{keep} & \text{otherwise}.
    \end{cases}
\end{equation}
The parameters $\Trefine > \Tdelete$ can be chosen freely.
Chebyshev's inequality
\begin{equation}
  \label{eq:chebychev}
  \mathbb{P}(\vert X - \mu \vert \geq c \sigma) \leq \frac{1}{c^2},
\end{equation}
with probability $\mathbb{P}$ guarantees that we neither refine nor delete all cells. \todo{LR: Was gibt es an compressible NS mit dynamic AMR, wie unterscheiden wir uns im Refinement Kriterium?}
This inequality holds for arbitrary distributions under the weak assumption that their mean $\mu$ and standard deviation $\sigma$ are finite~\cite{wasserman2004all}.
